Open-source tools in R for landscape ecology

### 2021-02-10 paper/paper.Rmd
Clean figures

ggplot_packages <- ggplot(data = r_packages_df) +
  geom_bar(aes(y = r_package_reclass, x = n_rel, fill = col), stat = "identity") +
  # geom_text(aes(y = r_package_reclass, x = n_rel, label = label, col = col),
  #           nudge_x = 2, size = 2.5) +
  theme_classic(base_size = base_size) +
  theme(plot.title.position = "plot") +
  scale_x_continuous(breaks = seq(0, 35, 5), limits = c(0, 36)) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_colour_manual(values = c("grey50", "black")) +
  guides(fill = FALSE, colour = FALSE) +
  labs(x = "Number of package mentioned [%]", y = NULL,
       title = "List the three*R packages related\nto landscape ecology you use the most")
```

>>>>

ggplot_packages <- ggplot(data = r_packages_df) +
  geom_bar(aes(y = r_package_reclass, x = n_rel, fill = col), stat = "identity") +
  # geom_text(aes(y = r_package_reclass, x = n_rel, label = label, col = col),
  #           nudge_x = 2, size = 2.5) +
  theme_classic(base_size = base_size) +
  theme(plot.title.position = "plot") +
  scale_x_continuous(breaks = seq(0, 35, 5), limits = c(0, 36)) +
  scale_fill_manual(values = c("grey50", "black")) +
  scale_colour_manual(values = c("grey50", "black")) +
  guides(fill = FALSE, colour = FALSE) +
  labs(x = "Number of package mentioned [%]", y = NULL,
       title = "List the three R packages related\nto landscape ecology you use the most")
```
